% In this file you should put the actual content of the blueprint.
% It will be used both by the web and the print version.
% It should *not* include the \begin{document}
%
% If you want to split the blueprint content into several files then
% the current file can be a simple sequence of \input. Otherwise It
% can start with a \section or \chapter for instance.

\section{WStarAlgebras and their Topologies}

In this section we define the topologies and need to prove that $W^{*}$--algebras are closed with respect to these. Must also put these
dependencies explicitly into the results that use them below. 

Maybe collect things into Basic CStar section and Basic WStar section?

\begin{lemma}
    \label{lem:sigma_closed_star_subalg_wstar} (Sakai 1.1.4)
  A self-adjoint, $\sigma$--closed $*$--subalgebra $N$ of a $W^{*}$--algebra $M$ is also a $W^{*}$--algebra, since $(M_{*}/N^{0})^{*}=N$, where
  $N^{0}$ is the polar (annihilator) of $N$ in $M_{*}$, i.e. the set of $\varphi\in M_{*}$ such that $\varphi(x)=0$ for all $x\in N$.
\end{lemma}

\begin{proof}
\end{proof}

\begin{lemma}
  \label{lem:cut_down_sigma_closed_cts} (Sakai 1.7.6)
  Let $p$ be any projection in $M$. Then the subalgebra $pMp$ is $\sigma$--closed and the mapping $x\mapsto pxp$ is $\sigma$--continuous.
\end{lemma}

\begin{proof}
\end{proof}

\begin{lemma}
  \label{lem:cut_down_of_wstar} 
  \uses{lem:cut_down_sigma_closed_cts,lem:sigma_closed_star_subalg_wstar}
  If $p\in M$ is a projection, $pMp$ is also a $W^{*}$algebra with identity $p$.
\end{lemma}

\begin{proof}
  It is clear that $eMe$ is an algebra, since any sum or product of elements preserves the pre and post multiplication by $e$.
  It is also clear that $e$ is the multiplicative identity of this algebra. The product reversing property of $*$ and the fact that
  $e$ is a self-adjoint projection implies that $eMe$ is a $*$--algebra. By Lemma \ref{lem:sigma_closed_star_subalg_wstar}, if this 
  $*$--subalgebra is $\sigma$--closed, then it is a $W^{*}$--subalgebra of $M$. But this is the result of \ref{lem:cut_down_sigma_closed_cts}.
\end{proof}

\section{Order Lemmas}

Let $\mathcal{A}$ be a unital $C^{*}$--algebra in this section. We collect lemmas for the ordering of elements in $\mathcal{A}$. 
Recall that a selfadjoint element $a \in \mathcal{A}$ is said to be \textbf{positive} if its spectrum is contained in $\mathbb{R}_{\ge 0}$. 
This is written $a\ge 0$. If $a,b \in \mathcal{A}$ are selfadjoint then $b \le a$ if $b-a \ge 0$.
(TO DO: adapt this to Jireh's fully general ordering on all elements without mentioning the selfadjoint ones.)

\begin{lemma}
  \label{lem:pos_iff_star_mul_self_Sak_1_4_4} (Sak 1.4.4)
  \lean{CStarAlgebra.nonneg_TFAE,StarOrderedRing.nonneg_iff}
  \leanok
  Let $h \in \mathcal{A}$. TFAE:
  \begin{enumerate}
  \item $h \ge 0$;
  \item There exists $x\in \mathcal{A}$ such that $h=x^{*}x$.
  \end{enumerate}
\end{lemma}

\begin{proof}
  \leanok
\end{proof}

\begin{corollary}
  \label{lem:star_conj_pos}
  \lean{star_left_conjugate_nonneg}
  \mathlibok
  \uses{lem:pos_iff_star_mul_self_Sak_1_4_4}
  If $h,a \in \mathcal{A}$ with $h\ge 0$ then $a^{*}ha\ge 0$
\end{corollary}

\begin{proof}
  \leanok
  By Lemma \ref{lem:pos_iff_star_mul_self_Sak_1_4_4}, $a^{*}ha=a^{*}x^{*}xa=(xa)^{*}(xa)\ge 0$.
\end{proof}

\begin{lemma}
  \label{lem:selfadjoint_le_norm}
  \lean{IsSelfAdjoint.le_algebraMap_norm_self}
  \leanok
  \mathlibok
  If $x\in \mathcal{A}$ is selfadjoint then $\|x\|1-x \ge 0$.
\end{lemma}

\begin{proof}
\leanok
\end{proof}

\section{Projection Lemmas}

Let $\mathcal{A}$ be a unital $C^{*}$--algebra in this section. In this section we collect relevant results about (selfadjoint) projections in $\mathcal{A}$. 
Recall that an element $p$ in a $C^{*}$--algebra is a projection if $p^2=p^{*}=p$. By the Spectral Mapping Theorem (or using the full Gelfand Duality),
a selfadjoint element $a\in A$ is a projection if and only if the spectrum of $a$ is contained in $\{0,1\}$.

\begin{lemma}
  \label{lem:proj_le_one}
  \lean{IsStarProjection.le_one}
  \mathlibok
  \uses{lem:selfadjoint_le_norm}
  For all projections $p\in \mathcal{A}$, $p \le 1$.
\end{lemma}

\begin{proof}
  \leanok
  We can get this by Sakai 1.2.3. and Lemma \ref{lem:selfadjoint_le_norm} We should include that result here.
\end{proof}

\begin{lemma}
  \label{lem:proj_sub_pos_iff_comm_eq_self}
  \lean{IsStarProjection.sub_tfae}
  \leanok
  \uses{lem:star_conj_pos, lem:proj_le_one}
  Let $\mathcal{A}$ be a $C^{*}$--algebra and $p,q \in \mathcal{A}$ be projections. Then $p-q\ge 0$ iff $qp = pq = q$.
\end{lemma}

\begin{proof}
  \leanok
  By Lemma \ref{lem:star_conj_pos}, if $p-q \ge 0$ then $q(p-q)q=qpq-q^3=qpq-q \ge 0$. By Lemma \ref{lem:proj_le_one}, we have $p\le 1$ and 
  employing Lemma \ref{lem:star_conj_pos} we obtain $qpq\le q1q=q$. Since $qpq\ge q$ and $qpq\le q$ we have $qpq=q$, which implies that $q(p-q)q=0$.
  By the $C^{*}$-property of the norm, we have $\|(p-q)^{1/2}q\|^2=\|q(p-q)q\|=0$ and so $(p-q)^{1/2}q=0$ and therefore $(p-q)q=(p-q)^{1/2}(p-q)^{1/2}q=0$.
  It follows that $pq=q$, and taking adjoints, $qp=q$.
  Conversely, if $qp=pq=q$, one easily checks that $p-q$ is a projection and so its spectrum is contained in $\{0,1\}$ and it is positive.
\end{proof}

\begin{corollary}
  \label{cor:proj_sub_of_subproj}
  \lean{IsStarProjection.sub_tfae}
  \leanok
  \uses{lem:proj_sub_pos_iff_comm_eq_self}
  For all $p,q \in \mathcal{A}$ projections such that $q\le p$, $p-q$ is a projection.
\end{corollary}

\begin{proof}
  \leanok
\end{proof}

\section{Positive Linear Functionals and States}

Will continue to chase results backwards in Sakai. Note that the norm on a $C^{*}$--algebra
is uniquely determined (we will include the needed results for this above and remove this
comment once we have). The following proposition characterizes it in terms of the states on 
$\mathcal{A}$, also establishing that states separate the elements of $\mathcal{A}$. Let
$\mathcal{S}$ denote the set of states on the appropriate $C^{*}$--algebra in the sequel.

\begin{proposition}
  \label{prop:norm_as_state_sup}
  Let $h$ be a self-adjoint element in a $C^{*}$--algebra $\mathcal{A}$.
  then $\|h\|=\sup_{\varphi\in \mathcal{S}}|\varphi(h)|$.
\end{proposition}

\begin{proof}
\end{proof}

Now let $M$ be a $W^{*}$--algebra and let $T$ denote the set of all $\sigma$--continuous positive
linear functionals on $M$, and $E$ the linear space of all finite linear combinations
of elements of $T$. Let $P$ and $M^{s}$ denote the set of positive elements and set of self-adjoint elements of $M$, respectively.

\begin{lemma}
  \label{lem:pos_cvx_cone}
  \lean{ConvexCone.positive}
  \mathlibok
  $P$ is a convex cone in $M$.
\end{lemma}

\begin{proof}
  \leanok
\end{proof}

\begin{lemma}
  \label{lem:pos_sa_sigma_closed}
  \lean{Ultraweak.isClosed_setOf_IsSelfAdjoint, Ultraweak.isClosed_nonneg}
  \leanok
  $P$ and $M^{s}$ are $\sigma$--closed.
\end{lemma}

\begin{proof}
  \leanok
\end{proof}

\begin{lemma}
  \label{lem:non_pos_elem_neg_for_some_state_Sak_1_7_2} (Sak 1.7.2)
  \uses{lem:pos_cvx_cone,lem:pos_sa_sigma_closed}
  For any self-adjoint element $a\notin P$, there exists $\varphi\in T$
  such that $\varphi(a)<0$.
\end{lemma}

\begin{proof}
  By Lemmas \ref{lem:pos_cvx_cone} and \ref{lem:pos_sa_sigma_closed}, $P$ is a $\sigma$--closed convex cone in 
  the real locally convex space $M^{s}$. By the Hahn-Banach Separation Theorem, there is a $\sigma$--continuous real linear functional $g$
  on $M^{s}$ such that $\inf_{h\in P}g(h)>g(a)$. Since $P$ is a cone, if $g(h)<0$ then we could scale $h$ by a positive constant so $g(ch)\le g(a)$, which
  is nonsense. Therefore $g(h)\ge 0$ for all $h\ge 0$, and the infimum above must be zero (which can again by seen by scaling). It follows that
  $0>g(a)$. To appropriately extend $g$ to a functional on $M$, define $\varphi(a + ib)=g(a)+ig(b)$ for any $a,b \in M^{s}$. This $\varphi$ is a (complex) linear 
  functional on $M$, and the $*$--operation is $\sigma$--continuous because $M^{s}$ is $\sigma$--closed (by Lemma \ref{lem:pos_sa_sigma_closed}).
  It follows that $\varphi$ is a $\sigma$--continuous positive linear functional on $M$ such that $\varphi(a)=g(a)<0$.
\end{proof}

\begin{lemma}
  \label{lem:uw_pos_sep_pts}
  \uses{lem:non_pos_elem_neg_for_some_state_Sak_1_7_2}
If $a\in M$, and $\psi(a)=0$ for every $\psi\in T$, then $a=0$.
\end{lemma}

\begin{proof}
  Given nonzero $a\in P$ in $M$, since $P$ is a cone, $-a \notin P$. By Lemma \ref{lem:non_pos_elem_neg_for_some_state_Sak_1_7_2}, there is
  a $\varphi\in T$ such that $\varphi(-a)<0$, hence $\varphi(a)>0$. The desired statement follows by contraposition.
\end{proof}

\section{Stonean Spaces and Maximal Commutative Subalgebras}

Recall that a compact Hausdorff space is \textbf{Stonean} if the closure of every open set is open. We note that Lemma
\ref{lem:fin_lin_approx_of_stonean_Sak_1_3_1} is only part of Sakai 1.3.1, since that is all
we need for the proof of Theorem \ref{thm:sigma_cts_of_normal}. If $K$ is a topological space in which singletons are closed,
and $p$ is a projection in $C(K)$, the spectrup of $p$ is its range and is contained in $\{0,1\}$.
Furthermore, $p^{-1}\{0\}=K\backslash p^{-1}\{1\}$, and so both of these sets are clopen, and identify connected components of $K$.
If $K$ is Stonean, there are many such connected components:

\begin{lemma}
  \label{lem:fin_lin_approx_of_stonean_Sak_1_3_1} (Sak  1.3.1)
  Let $K$ be a Stonean space. Then every positive self-adjoint element $a$ in $C(K)$ can be uniformly approximated by 
  finite linear combinations of projections in $C(K)$ having nonnegative coefficients. 
\end{lemma}

\begin{proof}
Since $a$ is self-adjoint, its spectrum is its range in $\mathbb{R}_{\ge 0}$, and is therefore contained in $[0, \|a\|]$,
where $\|a\|=\sup_{t\in K}|a(t)|$. Let $\varepsilon >0$ and choose real numbers
$0<\lambda_1<\lambda_2<\ldots<\lambda_n < \|a\|+1$ so that $|\lambda_{i+1}-\lambda_{i}|<\varepsilon$.
Now let $G_1= \overline{\{t\in K | a(t)<\lambda_1\}}$ and $G_i=\overline{\{t\in K
\backslash\bigcup_{j=1}^{i-1}G_{i}|a(t)<\lambda_i\}}$ for $i>1$. These are pairwise disjoint,
and $\chi_{G_{i}}$ are each continuous projections. Furthermore, for all $t\in K$,
\begin{align}
    |a(t)-\sum_{i=1}^{n}\lambda_i\chi_{G_{i}}(t)|<\varepsilon
\end{align}
and therefore $\|a-\sum_{i=1}^{n}\lambda_i\chi_{G_{i}}\|<\varepsilon$.
\end{proof}

In Sakai, the pointwise order on $C(K)$ in Proposition \ref{prop:stonean_of_cts_fcns_incr_cond_complete_Sak_1_3_2}
isn't specified beforehand in the book. Following $C^{*}$--algebra theory, $a\ge 0$ in $C(K)$
iff the range of $a$ is contained in $\mathbb{R}_{\ge 0}$, and $b\le a$ iff $b-a \ge 0$. The spectrum 
of a function in $C(K)$ is just its range. So $b\le a$ iff $b(t)\le a(t)$ for all $t\in K$. A net
 $(f_{\alpha})$ in $C(K)$ is \textbf{bounded} if there is a positive constant that bounds the norms of all $f_{\alpha}$.
A net is said to be \textbf{increasing} if $\alpha \le \beta$ implies $f_{\alpha}\le f_{\beta}$ for all $\alpha,\beta$
in the associated directed set. We ought to note, here, that Sakai opts not to use net language
(although he sort of does when introducing subscripts) since his directed set is identical to his net
in Proposition \ref{prop:stonean_of_cts_fcns_incr_cond_complete_Sak_1_3_2}. Recall that 
the \textbf{support} of $f\in C(K)$ is $\overline{\{x\in K | f(x)\ne 0\}}$.

\begin{lemma}
    \label{lem:cts_fns_ge_zero_le_one_directed}
    Let $K$ be a compact Hausdorff space, with $U\subseteq K$ open, then the set of $f\in C(K)$ supported on $U$ such that
    $0 \le f \le 1$ is a directed set w.r.t. the order on $C(K)$.
\end{lemma}

\begin{proof}
    The usual order is a partial order, and given $f,g\in C(K)$ supported on $U$ we have $f\vee g \in C(K)$, 
    supported on $U$, where $f\vee g(t)=\max\{f(t),g(t)\}$.
\end{proof}

\begin{proposition}
    \label{prop:stonean_of_cts_fcns_incr_cond_complete_Sak_1_3_2} (Sakai 1.3.2)
    \uses{lem:cts_fns_ge_zero_le_one_directed,lem:selfadjoint_le_norm}
    Let $K$ be a compact Hausdorff space. Suppose every bounded increasing net
    of real valued, non-negative functions in $C(K)$ has a least upper bound in $C(K)$.
    Then $K$ is Stonean. 
\end{proposition}

\begin{proof}
    Suppose for the sake of a contradiction that $K$ isn't Stonean, i.e. that there exists an
    open set $U$ whose closure isn't open, i.e. that $\overline{U}^{c}$ isn't closed.
    Consider the set of $f$ in $C(K)$ with support contained in $U$ and such that $0\le f\le 1$. 
    By Lemma \ref{lem:selfadjoint_le_norm} and Lemma \ref{lem:cts_fns_ge_zero_le_one_directed}, 
    this is a bounded, increasing net with respect to the order on $C(K)$. 
    For any point $t\in U$, by Urysohn's Lemma (compact Hausdorff Spaces are regular) there
    exists a continuous function $g\in C(K)$ such that $g(t)=1$ and $g$ is zero on $U^{c}$. 
    It follows that if $f_s$ is the least upper bound of the above net, then $1=g(t)\le f_s(t)$, 
    and therefore (since we can play this game for any $t\in U$) it must be that $f_s(t)=1$ for any $t\in U$. 
    By continuity, $f_s(t)=1$ for all $t\in\overline{U}$. Now, since $\overline{U}^{c}\subset U^{c}$, 
    $f_c$ is identically zero on $U^{c}$. Since $\overline{U}^{c}$ is not closed, it must have a limit point
    $p\in \overline{U}$, and by continuity $f_c(p)=0$ But $f_c(p)=1$ by the above, which is a contradiction.
\end{proof}

\begin{lemma}
  \label{lem:spec_masa_wstar_stonean_Sak_1_7_5} (Sak 1.7.5)
  \uses{prop:stonean_of_cts_fcns_incr_cond_complete_Sak_1_3_2}
  If $C$ is any maximal commutative $C^*$--subalgebra of the $W^{*}$--algebra $M$, its
  spectrum space (maximal ideal space) is Stonean.
\end{lemma}

\begin{proof}
  Suppose $(a_{\lambda})$ is a uniformly bounded, increasing net of positive elements in $C$ with supremum $a$. 
  Given any unitary $u\in C$, we have $u^{*}\sup_{\lambda}a_{\lambda} u=\sup_{\lambda}u^{*}a_{\lambda}u$ and since every
  element in $C$ is a linear combination of unitary elements from $C$, we have that $sup_{\lambda}a_{\lambda}\in C$. The result
  follows from Proposition \ref{prop:stonean_of_cts_fcns_incr_cond_complete_Sak_1_3_2} after applying the Gelfand transform.
\end{proof}

\section{Normality and Ultraweak Continuity for Positive Functionals}

In what follows, let $M$ be a (nonzero) $W^{*}$--algebra. Let $\mathcal{P}(M)$
denote the projection lattice of $M$. Let $\varphi$ be a positive linear functional $\varphi$ on $M$.
We say $\varphi$ is \textbf{normal} if whenever $(p_{\alpha})$ is an increasing net of projections in $M$ with supremum $p$,
we have $\varphi(p_{\alpha})\to \varphi(p)$. In this section we show that this property is equivalent to 
$\sigma(M, M_{*})$--continuity. We say that a linear functional $\varphi$ on $M$
is \textbf{positive} if $\varphi(x)\ge 0$ whenever $x\ge 0$.

\subsection{Ultraweakly Continuous Implies Normal} 

In what follows, let $T$ denote the set of all $\sigma$--continuous positive
linear functionals on $M$, and $E$ the linear space of all finite linear combinations
of elements of $T$. Let $P$ denote the set of positive elements of $M$.

\begin{lemma}
  \label{lem:homeo_of_cts_bij_cpt_haus}
  \lean{isHomeomorph_iff_continuous_bijective}
  \mathlibok
  Every continuous bijection from a compact space to a Hausdorff space is a 
  homeomorphism.
\end{lemma}

\begin{proof}
  \leanok
  Omitted. In Mathlib.
\end{proof}

\begin{theorem}
  \label{thm:Banach_Alaoglu}
  \lean{WeakDual.isCompact_closedBall}
  \mathlibok
  (Banach-Alaoglu) The closed unit ball of the dual space of a normed vector space is compact in the
  weak-$*$ topology.
\end{theorem}

\begin{proof}
  \leanok
  Omitted. In Mathlib.
\end{proof}

\begin{theorem}
  \label{lem:sigma_cont_of_normal_Sak_1_7_4}
  \uses{thm:Banach_Alaoglu,lem:homeo_of_cts_bij_cpt_haus,lem:uw_pos_sep_pts}
  Every uniformly bounded, increasing directed set converges
  to its least upper bound in the $\sigma$--topology. Further, if
  $x=\sup_{\alpha}x_\alpha$ then $a^{*}xa=\sup_{\alpha}a^{*}xa$.
\end{theorem}

\begin{proof}
\end{proof}

\subsection{Normal Implies Ultraweakly Continuous}

\begin{lemma}
  \label{lem:proj_of_sup_proj}
  For every increasing bounded net $(p_{\alpha})$ of projections in $M$, the supremum $p$
  is a projection in $M$
\end{lemma}

\begin{proof}
\end{proof}

If $P:\mathcal{P}(M)\to \text{Prop}$ is a predicate, the usual ordering ``$\le$'' on projections
induces an order on the set $\{p\in \mathcal{P}(M)|P(p)\}$. In what follows there will be no confusion if 
we also denote this induced order by ``$\le$''.

\begin{lemma}
  \label{lem:exists_uw_ge_normal}
  \uses{lem:uw_pos_sep_pts}
  For every positive normal linear functional $\varphi$ and nonzero $p\in \mathcal{P}(M)$
  there exists a positive $\sigma(M,M_{*})$--continuous linear functional $\psi$ such that $\varphi(p)<\psi(p)$.
\end{lemma}

\begin{proof}
  By Lemma \ref{lem:uw_pos_sep_pts} there is a $\sigma(M,M_{*})$--continuous positive linear
  functional $\psi_0$ on $M$ such that $\psi_0(p)\ne 0$. Rescale this functional by a positive constant to obtain
  $\psi$ such that $\varphi(p)<\psi(p)$.
\end{proof}

\begin{lemma}
  \label{lem:msr_th_lemma}
  \uses{lem:sigma_cont_of_normal_Sak_1_7_4,lem:proj_of_sup_proj,cor:proj_sub_of_subproj}
For all positive linear functionals $\varphi,\psi$ with
$\varphi$ normal and $\psi$ $\sigma(M,M_{*})$--continuous and every nonzero $p\in \mathcal{P}(M)$
such that $\varphi(p)<\psi(p)$, there exists a nonzero $p_1 \in \mathcal{P}(M)$ such that $p_1\le p$ and for all nonzero
$q\in \mathcal{P}(M)$ with $q\le p_1$, we have $\varphi(q)<\psi(q)$. 
\end{lemma}

\begin{proof}
  We proceed by contradiction. Suppose the conclusion does not hold. Then, for every nonzero subprojection
  $p_1$ of $p$ there is a nonzero subprojection $q\le p_1$ such that $\varphi(q)\ge \psi(q)$. In particular,
  (letting $p_1=q$) there is a $q\le p$ such that $\varphi(q)\ge \psi(q)$. If $(q_\alpha)$ is a chain
  of such nonzero projections, $q_{\alpha}\to \sup q_{\alpha}$ in the $\sigma$--topology by Theorem \ref{lem:sigma_cont_of_normal_Sak_1_7_4}, 
  and by Lemma \ref{lem:proj_of_sup_proj} we know this supremum is a subprojection of $p_1$. Since $\varphi$
  is positive and normal, and $\psi$ is positive and $\sigma$--continuous, we have $\varphi(\sup q_{\alpha})\ge \psi(\sup q_{\alpha})$.
  Therefore, by Zorn's Lemma, there is a maximal $q_{0}\le p$ such that $\varphi(q_0)\ge \psi(q_0)$. We claim $q_{0}=p$. If not, 
  $p-q_0$ is a nonzero subprojection of $p$ by Corollary \ref{cor:proj_sub_of_subproj}, and there exists a nonzero projection $q_{1}\le p-q_{0}$
  such that $\varphi(q_{1})\ge \psi(q_{1})$. But then $q_{0}$ is a proper subprojection of $q_0+q_1$ and by linearity and positivity 
  $\varphi(q_0+q_1)\ge \psi(q_0+q_1)$ contradicting the maximality of $q_0$. Thus $p=q_0$ and so $\varphi(p) \ge \psi(p)$, contradicting 
  the hypothesis $\varphi(p)<\psi(p)$.  
\end{proof}

Note that the following likely contains the most crucial use of the normality of $\varphi$ for the later proof 
of Theorem \ref{thm:sigma_cts_of_normal}.

\begin{lemma}
  \label{lem:zorn_base}
  \uses{cor:proj_sub_of_subproj,lem:selfadjoint_le_norm,lem:sigma_cont_of_normal_Sak_1_7_4,lem:proj_of_sup_proj}
  Let $\varphi$ be a normal positive linear functional on $M$ and consider the predicate $P:\mathcal{P}(M)\to \text{Prop}$ defined, for $p\in \mathcal{P}(M)$, by 
  ``$M\ni x \mapsto \varphi(xp)$ is $\sigma(M,M_{*})$--continuous''. If $(p_{\alpha})$ is a chain of projections in $M$ such that $P(p_{\alpha})$ is true for each $\alpha$,
  then $P(\sup(p_{\alpha}))$ is true. Hence by Zorn's Lemma there is a maximal $p_0\in \mathcal{P}(M)$ such that $P(p_0)$ is true.  
\end{lemma}

\begin{proof}
  Let $x$ be on the unit sphere and let $p$ be the supremum of the $p_{\alpha}$. By Theorem \ref{lem:sigma_cont_of_normal_Sak_1_7_4} and Lemma \ref{lem:proj_of_sup_proj} 
  we know $p_{\alpha}$ converges in $\sigma$--topology to $p$, and $p$ is a projection. 
  By Corollary \ref{cor:proj_sub_of_subproj} we know $p-p_\alpha$ is a projection. By the $C^{*}$--property
  of the norm ($\|x^{*}x\|=\|x\|^{2}$), Lemma \ref{lem:selfadjoint_le_norm} and the positivity of $\varphi$ we have $\varphi(x^{*}x)\le \varphi(1)$.
  Now these facts together with Cauchy-Schwartz and the monotonicity of square roots, 
  \begin{align}
    |\varphi(x(p-p_{\alpha}))|&\le \varphi(x^{*}x)^{1/2}\varphi(p-p_{\alpha})^{1/2}\\ \nonumber
    &\le \varphi(1)^{1/2}\varphi(p-p_{\alpha})^{1/2}.
  \end{align}
  Hence, by the definition of operator norm, $\|\varphi(\cdot(p-p_{\alpha}))\|\le \varphi(1)^{1/2}\varphi(p-p_{\alpha})^{1/2}$. The right
  hand side converges to 0 with $\alpha$ due to the normality of $\varphi$ and therefore $\varphi(\cdot p_{\alpha})$ converges to $\varphi(\cdot p)$
  in norm. Since the set of $\sigma$--continuous functionals on $M$ is norm closed, it follows that $\sigma(\cdot p)$ is $\sigma$--continuous.
  We obtain a maximal $p_{0}$ by Zorn's Lemma.
\end{proof}

\begin{lemma}
  \label{lem:bdd_sigma_cts_iff_bdd_s_cts_Sak_1_8_10} (Sak 1.8.10)
  A linear functional $\rho$ on $M$ is $\sigma$--continuous on the unit sphere (hence $\sigma$--continuous) if and only if it is $s$--continuous on the
  unit sphere (hence $s$--continuous).
\end{lemma}

\begin{proof}
\end{proof}

\begin{lemma}
  \label{lem:wstar_of_masa}
  A maximal abelian $*$--subalgebra of a $W^{*}$--algebra $M$ is also a $W^{*}$--algebra.
\end{lemma}

\begin{proof}
\end{proof}

\begin{theorem}
  \label{thm:sigma_cts_of_normal}
  \uses{lem:zorn_base,lem:exists_uw_ge_normal,lem:msr_th_lemma,lem:cut_down_of_wstar,lem:spec_masa_wstar_stonean_Sak_1_7_5,lem:fin_lin_approx_of_stonean_Sak_1_3_1,lem:bdd_sigma_cts_iff_bdd_s_cts_Sak_1_8_10,lem:wstar_of_masa}
  Every positive normal linear functional $\varphi$ on $M$ is $\sigma(M,M_{*})$--continuous.
\end{theorem}

\begin{proof}
  The claim is obvious for the zero functional. Let $\varphi$ be a nonzero positive normal linear functional. By Lemma \ref{lem:zorn_base} we have
  a maximal $p_0\in \mathcal{P}(M)$ such that $M\ni x \mapsto \varphi(xp_0)$ is $\sigma(M,M_{*})$--continuous. Assume for the purposes of finding
  a contradiction that $p_0\ne 1$. By Lemma \ref{lem:exists_uw_ge_normal}
  there is a $\sigma(M,M_{*})$--continuous positive functional $\psi$ on $M$ such that $\varphi(1-p_0)<\psi(1-p_0)$. By Lemma \ref{lem:msr_th_lemma}
  there is a nonzero subprojection $p\le 1-p_0$ in $M$ such that $\varphi(q)< \psi(q)$ for every nonzero $q\le p$ in $M$. Let $x\in pMp$ be on the unit sphere. 
  Then $x^{*}x$ is positive and hence normal, so the $C^{*}$--subalgebra of $pMp$ generated by $x^{*}x$ and $p$ is commutative, and is hence contained in a maximal abelian
  $*$--subalgebra $A$ of $pMp$. Now $A$ is a $W^{*}$--subalgebra of $pMp$ by Lemma \ref{lem:wstar_of_masa} and hence is a maximal commutative $C^{*}$--subalgebra of $pMp$. Via the Gelfand Transform, 
  $A$ is star isomorphic to $C(K)$, where $K$ is Stonean by Lemmas \ref{lem:cut_down_of_wstar} and \ref{lem:spec_masa_wstar_stonean_Sak_1_7_5}. 
  By Lemma \ref{lem:fin_lin_approx_of_stonean_Sak_1_3_1} it follows that $\varphi(a)\le \psi(a)$ for every $a\ge 0$ in $A$, which holds a fortiori for $a\ge 0$ in $C^{*}(x^{*}x,p)$. 
  In particular, $\varphi(px^{*}xp)\le \psi(px^{*}xp)$. Therefore,
  \begin{align}
    |\varphi(x(p_0+p))|&\le |\varphi(xp_0)|+|\varphi(xp)|\\ \nonumber
    &\le |\varphi(xp_0)|+\varphi(1)^{1/2}\varphi(px^{*}xp)^{1/2}\\ \nonumber
    &\le |\varphi(xp_0)|+\varphi(1)^{1/2}\psi(px^{*}xp)^{1/2}.
  \end{align}
  Since $x\mapsto \varphi(xp_0)$ is $\sigma$--continuous, it is $s$-continuous by Lemma \ref{lem:bdd_sigma_cts_iff_bdd_s_cts_Sak_1_8_10}. The seminorm
  $x \mapsto \psi(px^{*}xp)^{1/2}$ is a defining seminorm for the $s$--topology on $M$. It follows that $x\mapsto \varphi(x(p_0+p))$ is $s$-continuous
  and therefore $\sigma$--continuous. This contradicts the maximality of $p_0$, and therefore $p_0=1$ and the result follows. 
\end{proof}